Cap-and-trade in Energy Capacity Investment when the planner is inattentive

### 2022-07-15 docs/Presentations/UVigo/home.Rmd
uvigo final

$$C(P)=\begin{cases}0,&P\leq d\\c(P-d)^2,&P>d\end{cases},$$

where $P\in[0,1]$ is a performance metric, $c$ an associated marginal cost and $d$ the performance level wiht public information.

@@

- $\min_{(\theta,P)\in[0,(1+\epsilon)CAP]\times[0,1]}-\theta\pi^aP+c(P-d)^2$ profit oriented
- $\min_{\theta\in[0,CAP]}-\theta\pi^a+c\left(1-\frac{|\theta-CAP|}{CAP}-d\right)^2$ welfare oriented
---
name: results
# Results: Profit oriented

- Calibration wrt `r Citet(mybib, "amigo_two_2021")`
  - CAP: $100 MtCO_2$
  - $\pi^a=315.83$
  - $\epsilon=0.202$ Andres et alii (2014)
$$\Rightarrow c=920M$$

---
name: remarks
# Final Remarks

- Multiple solutions and comparative statics

@@

.pull-left[
.small[
```{r refsI, echo=FALSE, results="asis"}
PrintBibliography(mybib, .opts = list(check.entries = TRUE), start=1, end=3)
```
]
]

@@

```{r refsII, echo=FALSE, results="asis"}
PrintBibliography(mybib, .opts = list(check.entries = TRUE), start=4, end=6)
```
]
]

>>>>

$$C(P)=\begin{cases}0,&Perf\leq d\\c(Perf-d)^2,&Perf>d\end{cases},$$

where $Perf\in[0,1]$ is a performance metric, $c$ an associated marginal cost and $d$ the performance level wiht public information.

@@

- $\min_{(\theta,Perf)\in[0,(1+\epsilon)CAP]\times[0,1]}-\theta\pi^aPerf+c(Perf-d)^2$ profit oriented
- $\min_{\theta\in[0,CAP]}-\theta\pi^a+c\left(1-\frac{|\theta-CAP|}{CAP}-d\right)^2$ welfare oriented
---
name: results
# Results: Profit oriented
.pull-left[
- Calibration wrt `r Citet(mybib, "amigo_two_2021")`
  - CAP: $100 MtCO_2$
  - $\pi^a=315.83$
  - $\epsilon=0.202$ Andres et alii (2014)
$$\Rightarrow c=920M$$ 
]
.pull-right.center[
$CAP=100$

| Perf | $\theta$    | $\frac{\theta}{CAP}$ | $\pi^a$  |
|---------|-------------|----------------------|----------|
| 0.798   | 120,200,000 | 1.20                 | 270.13 |
| 0.8     | 120,200,000 | 1.20                 | 270.13 |
| 0.85    | 113,654,321 | 1.14                 | 25.75  |
| 0.9     | 113,568,965 | 1.14                 | 93.65  |
| 0.95    | 118,470,479 | 1.18                 | 188.86 |
| 0.99    | 114,916,396 | 1.15                 | 298.11 |
| 1       | 118,332,486 | 1.18                 | 317.24 |
]

---
# Results: Profit oriented and multiple CAPs, $Perf=0.8$

| CAP           | $\theta$    | $\frac{\theta}{CAP}$ | $\pi^a$  |
|---------------|-------------|----------------------|----------|
| 100,000,000   | 120,200,000 | 1.20                 | 270.13 |
| 200,000,000   | 240,400,000 | 1.20                 | 60.57  |
| 300,000,000   | 360,600,000 | 1.20                 | 119.47 |
| 400,000,000   | 454,798,037 | 1.14                 | 95.83  |
| 500,000,000   | 601,000,000 | 1.20                 | 79.31  |
| 600,000,000   | 605,279,899 | 1.01                 | 66.57  |
| 700,000,000   | 605,279,899 | 0.86                 | 56.37  |
| 800,000,000   | 961,600,000 | 1.20                 | 152.50 |
| 900,000,000   | 605,279,899 | 0.67                 | 42.26  |
| 1,000,000,000 | 605,279,899 | 0.61                 | 35.98  |
---
# Results: Profit oriented, allowances distributions

.pull-left[
```{r dist1, out.width="100%"}
knitr::include_graphics("diststage1.png")
```
]

.pull-right[
```{r dist2, out.width="100%"}
knitr::include_graphics("diststage2.png")
```
]

---
name: resultsW
# Results: Welfare oriented
.pull-left[
- Calibration wrt `r Citet(mybib, "amigo_two_2021")`
  - CAP: $100 MtCO_2$
  - $\pi^a=315.83$

$$\Rightarrow c=9920M$$ 
]
.pull-right.center[
| CAP  (M)         | $\theta$    | Perf | $\frac{\theta}{CAP}$ | $\pi^a$  |
|---------------|-------------|---------|----------------------|----------|
| 100   | 144,944,410 | 0.798   | 1.449                | 232.82 |
| 200   | 289,888,820 | 0.798   | 1.449                | 141.56 |
| 300   | 434,833,230 | 0.798   | 1.449                | 103.33 |
| 400   | 579,777,640 | 0.798   | 1.449                |    |
| 500   | 653,754,577 | 0.905   | 1.308                | 37.27  |
| 600   | 619,939,821 | 0.999   | 1.033                | 40.43  |
| 700   | 661,258,561 | 0.997   | 0.945                | 36.42  |
| 800   | 610,913,181 | 0.944   | 0.764                | 31.28  |
| 900   | 609,127,279 | 0.896   | 0.677                | 31.21  |
| 1,000 | 698,676,376 | 0.909   | 0.699                | 30.00  |
]
---
class: middle
name: remarks
# Final Remarks

- Respect of aggregate demand law
- Unclear relation of inattention
- Multiple solutions and comparative statics

@@

.pull-left[
.small[
```{r refsI, echo=FALSE, results="asis"}
PrintBibliography(mybib, .opts = list(check.entries = TRUE), start=1, end=2)
```
]
]

@@

```{r refsII, echo=FALSE, results="asis"}
PrintBibliography(mybib, .opts = list(check.entries = TRUE), start=3, end=5)
```
]
]

---
name: references2
# References II

```{r refsIII, echo=FALSE, results="asis"}
PrintBibliography(mybib, .opts = list(check.entries = TRUE), start=6, end=7)
```
